Supporting Information: Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2020-01-03 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Updates to figures

\title{Supporting Information: Time Series Modeling of Solute Transport in an H\textsubscript{II} 
Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \caption{The first column provides the names of the python scripts available in
  the \texttt{LLC\_Membranes} GitHub repository that were used for system setup and
  post-simulation trajectory analysis. Paths preceding script names are relative to the
  \texttt{LLC\_Membranes/LLC\_Membranes} directory. The second columns lists the section in the main
  text where the output or usage of the script is first described. The third column
  gives a brief description of the purpose of each script.
  }~\label{table:python_scripts}

@@

@@

  \subsection{Truncated L\'evy stable hop distributions}\label{section:truncation}

@@

  To derive an analytical equation for the mean first passage time 
  (Equation~\ref{M-eqn:passage_times} of the main text), first consider an 
  initial pulse spreading out over time with a fixed mean. We can solve for the 
  time-dependent probability density of particle positions, $p$, by solving the one
  dimensional diffusion equation:
  \begin{equation}
  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
  \end{equation}
  The appropriate initial and boundary conditions are:
  $$BC1: t > 0, z = \infty, p = 0$$
  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
  $$IC: t = 0, c = M\delta(z)$$
  where $M$ is the total number of particles in the system. It has been shown 
  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
  \end{equation}
  We can make the substitution $z = z - vt$, where $v$ represents a constant average
  velocity, in order to linearly shift the mean as a function of time:
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
  \end{equation}
  One can track the fraction of particles, $F$, that have crossed the pore 
  boundary by integrating:
  \begin{equation}
  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
  \end{equation}
  where $L$ is the pore length. This represents the cumulative first passage 
  time distribution so we take its derivative in order to arrive at the first
  passage time distribution:
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. We calculated the
  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT. Specifically,
  we used the python package \texttt{scipy.integrate.quad} to numerically integrate:
  \begin{equation}
  E[t] = \int_0^\infty tP(t) dt
  \end{equation}

>>>>

\title{Supporting Information: Time Series Modeling of Varying Complexity Captures 
Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \caption{The first column provides the names of the python scripts available in
  the \texttt{LLC\_Membranes} GitHub repository that were used for system setup and
  post-simulation trajectory analysis. Paths preceding script names are relative to the
  \texttt{LLC\_Membranes/LLC\_Membranes} directory. The second column lists the section in the main
  text where the output or usage of the script is first described. The third column
  gives a brief description of the purpose of each script.
  }~\label{table:python_scripts}

@@

  %Note that the partition of acetic acid appears
  %to be oscillating slowly. We do not expect the system to plateau on a
  %reasonable time scale, so we settled for including a complete oscillation.

@@

  % ordered this way to be consistent with mentions in the main text
  \subsection{Truncated L\'evy stable hop distributions}\label{section:truncation}

@@

  To derive an analytical equation for the mean first passage time 
  (Equation~\ref{M-eqn:passage_times} of the main text), first consider an 
  initial pulse spreading out over time with a fixed mean. We can solve for the 
  time-dependent probability density of particle positions, $p$, by solving the one
  dimensional diffusion equation:
  \begin{equation}
  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
  \end{equation}
  The appropriate initial and boundary conditions are:
  $$BC1: t > 0, z = \infty, p = 0$$
  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
  $$IC: t = 0, c = \delta(z)$$ % M\delta(z)
  %where $M$ is the total number of particles in the system. 
  It has been shown 
  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
  \end{equation}
  We can make the substitution $z = z - vt$, where $v$ represents a constant average
  velocity, in order to linearly shift the mean as a function of time:
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
  \end{equation}
  One can track the fraction of particles, $F$, that have crossed the pore 
  boundary by integrating:
  \begin{equation}
  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
  \end{equation}
  where $L$ is the pore length. This represents the cumulative first passage 
  time distribution so we take its derivative in order to arrive at the first
  passage time distribution:
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. We calculated the
  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT. Specifically,
  we used the python package \texttt{scipy.integrate.quad} to numerically integrate:
  \begin{equation}
  E[t] = \int_0^\infty tP(t) dt
  \end{equation}
